---
name: 
surname: František Bartoš
date: "`r format(Sys.time(), '%B, %Y')`"
position: "Postdoctoral Researcher, CFO of JASP Services"
address: "Amsterdam, Netherlands"
email: "f.bartos96@gmail.com"
www: "frantisek-bartos.info/"
github: "FBartos"
linkedin: "franti%C5%A1ek-barto%C5%A1-50249b192/"
headcolor: "414141"
csl: apa.csl
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
source("_functions.R")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# About

\begin{cvparagraph}
I am a postdoctoral researcher at the department of Psychological Methods at the University of Amsterdam and cofounder \& CFO of JASP Services. My goal is to improve statistical procedures and enable researchers to draw better inferences from data. I am interested in Bayesian statistics, meta-analyses, publication bias, and replicability. I also flipped some coins a couple of times.

\href{https://orcid.org/0000-0002-0018-5573}{OrcID: 0000-0002-0018-5573}, \href{https://www.webofscience.com/wos/author/record/ABD-1217-2021}{ResearcherID: ABD-1217-2021}, \href{https://scholar.google.com/citations?user=vAo-APsAAAAJ\&hl=en}{Google Scholar: vAo-APsAAAAJ}
\end{cvparagraph}

# Education

```{r education, results='asis'}
print_education_brief(read_cv_csv("education.csv"))
```

# Employment

```{r experience, results='asis'}
print_experience_brief(read_cv_csv("experience_brief.csv"))
```

# Funding

```{r funding, results='asis'}
print_funding(read_cv_csv("funding.csv"))
```

# Supervision

```{r supervision, results='asis'}
print_supervision(read_cv_csv("supervision.csv"))
```

# Teaching

```{r teaching, results='asis'}
print_teaching(read_cv_csv("teaching.csv"))
```

# Peer Review

```{r peer-review, results='asis'}
print_peer_review_inline(read_csv("peer_review.csv", show_col_types = FALSE))
```

# Scientific Societies

```{r societies, results='asis'}
print_peer_review_inline(read_csv("societies.csv", show_col_types = FALSE))
```

# Organization

```{r service-entries, results='asis'}
print_service_brief(read_cv_csv("service.csv"))
```

# Awards

```{r awards, results='asis'}
print_awards(read_cv_csv("awards.csv"))
```

# Scholarships

```{r scholarships, results='asis'}
print_scholarships(read_cv_csv("scholarships.csv"))
```


