---
name: 
surname: František Bartoš
date: "`r format(Sys.time(), '%B, %Y')`"
position: "Postdoctoral Researcher, CFO of JASP Services"
address: "Amsterdam, Netherlands"
email: "f.bartos96@gmail.com"
www: "frantisek-bartos.info/"
github: "FBartos"
linkedin: "franti%C5%A1ek-barto%C5%A1-50249b192/"
headcolor: "414141"
csl: apa.csl
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
source("_functions.R")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# About

\begin{cvparagraph}
I am a postdoctoral researcher at the department of Psychological Methods at the University of Amsterdam and cofounder \& CFO of JASP Services. My goal is to improve statistical procedures and enable researchers to draw better inferences from data. I am interested in Bayesian statistics, meta-analyses, publication bias, and replicability. I also flipped some coins a couple of times.
\end{cvparagraph}

# Education

```{r education}
read_cv_csv("education.csv") %>%
  mutate(details = strsplit(details, "\\|")) %>%
  detailed_entries(degree, dates, uni, loc, details)
```

# Employment & Experience

```{r experience}
read_cv_csv("experience.csv") %>%
  mutate(details = strsplit(details, "\\|")) %>%
  detailed_entries(role, dates, company, loc, details)
```

# Publications

## Meta-Analysis & Publication Bias Methods

```{r publications-meta, results='asis'}
print_publications("publications-meta_analysis.bib")
```

## Statistical Methods & Theory

```{r publications-statistics, results='asis'}
print_publications("publications-statistics.bib")
```

## Empirical Research & Meta-Science

```{r publications-empirical, results='asis'}
print_publications("publications-empirical.bib")
```

## Other Publications

```{r publications-other, results='asis'}
print_publications("publications-all.bib")
```

## Other Preprints

```{r publications-preprints, results='asis'}
print_publications("publications-preprints.bib")
```

# Software

\begin{cvparagraph}
My research output includes the development of open-source R packages for statistical analysis. These packages enable scientific practitioners to apply the developed methodology in practice.
\end{cvparagraph}

```{r software, results='asis'}
print_software(read_csv("software.csv", show_col_types = FALSE))
```

# Teaching

```{r teaching, results='asis'}
print_teaching(read_cv_csv("teaching.csv"))
```

# Supervision

```{r supervision, results='asis'}
print_supervision(read_cv_csv("supervision.csv"))
```

# Talks \& Workshops

## Keynotes

```{r keynotes-talks, results='asis'}
print_talks(read_cv_csv("talks_keynote.csv"))
```

## Invited

```{r invited-talks, results='asis'}
print_talks(read_cv_csv("talks_invited.csv"))
```

## Talks 

```{r conference-talks, results='asis'}
print_conference_talks(read_cv_csv("talks_conference.csv"))
```

## Workshops 

```{r workshops-talks, results='asis'}
print_workshops(read_cv_csv("workshops.csv"))
```

# Funding, Awards \& Scholarships

## Funding

```{r funding, results='asis'}
print_funding(read_cv_csv("funding.csv"))
```

## Awards

```{r awards, results='asis'}
print_awards(read_cv_csv("awards.csv"))
```

## Scholarships

```{r scholarships, results='asis'}
print_scholarships(read_cv_csv("scholarships.csv"))
```

# Service

## Organization

```{r service-entries, results='asis'}
print_service(read_cv_csv("service.csv"))
```

## Peer Review

```{r peer-review, results='asis'}
print_peer_review(read_csv("peer_review.csv", show_col_types = FALSE))
```
