---
name: 
surname: František Bartoš
date: "`r format(Sys.time(), '%B, %Y')`"
position: "PhD Candidate in Psychology, CFO of JASP Services"
address: "Amsterdam, Netherlands"
email: "f.bartos96@gmail.com"
www: "frantisek-bartos.info/"
github: "FBartos"
linkedin: "franti%C5%A1ek-barto%C5%A1-50249b192/"
headcolor: "414141"
csl: apa.csl
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
source("_functions.R")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# About

\begin{cvparagraph}
I am a Psychological Methods PhD candidate at the University of Amsterdam and cofounder \& CFO of JASP Services. My goal is to improve statistical procedures and enable researchers to draw better inferences from data. I am interested in Bayesian statistics, meta-analyses, publication bias, and replicability. I also flipped some coins a couple of times.
\end{cvparagraph}

# Education

```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "PhD Candidate in Psychology", "University of Amsterdam", "Amsterdam, Netherlands", "2021 - Present", 
    list("Research focus on Bayesian hypothesis testing, Bayesian model-averaging, meta-analyses, and publication bias adjustment.",
         "Developing novel statistical methods for meta-analytic inference in the presence of publication bias.",
         "Creating open-source software packages and contributing to the development of JASP."),
  "Research Master's in Psychology", "University of Amsterdam", "Amsterdam, Netherlands", "2019 - 2021", 
    list("Thesis published as F Bartoš, F Aust, JM Haaf (2022). Informed Bayesian survival analysis. BMC Medical Research Methodology, 22(1), 1-22.",
         "Internship published as F Bartoš, M Maier, D Quintana, EJ Wagenmakers (2022). Adjusting for publication bias in JASP and R: Selection models, PET-PEESE, and robust Bayesian meta-analysis. Advances in Methods and Practices in Psychological Science, 5(3), 1-19."),
  "Bachelor's Degree in Psychology", "Faculty of Arts, Charles University", "Prague, Czech Republic", "2016 - 2019", 
    list("Thesis Faktory asociovane s podvadenim (Factors associated with dishonesty) partially published as: F Bartoš (2024). The untrustworthy evidence in dishonesty research. Meta-Psychology, 8, 1-7.")
) %>% 
  detailed_entries(degree, dates, uni, loc, details)
```

# Experience

```{r experience}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Co-founder & Chief Financial Officer", "JASP Services", "Amsterdam, Netherlands", "2025 - Present",
    list("Co-founded commercial entity to support JASP statistical software development and sustainability.",
         "Managing financial operations and business strategy."),
  "Research Scientist", "Faculty of Social Sciences, Charles University", "Prague, Czech Republic", "2024 - 2025",
    list("Development of publication bias adjustment methodology for meta-analyses in economics."),
  "PhD Fellow", "Institute of Computer Science, Czech Academy of Sciences", "Prague, Czech Republic", "2022 - Present",
    list("Collaborating on research focused on inter-rater reliability.",
         "Developing statistical methods for assessing agreement and reliability in behavioral coding.",
         "Contributing to methodological advances in psychometrics."),
  "Research Assistant", "JASP Development Team", "Amsterdam, Netherlands", "2019 - 2021",
    list("R developer for JASP Development Team.",
         "Implemented Learn Bayes and Mixed Effects modules.",
         "Developed publication bias correction methods for the Meta-Analysis module."),
  "Research Assistant", "Center for Educational Measurement and Psychometrics, Charles University", "Prague, Czech Republic", "2018 - 2022",
    list("Collaborated with the Institute of Computer Science on project 'Testing heterogeneity in inter-rater reliability'.",
         "Developed Bayesian methodology for assessing heterogeneity in inter-rater reliability."),
  "Research Assistant", "Prague Laboratory for Experimental Social Sciences", "Prague, Czech Republic", "2017 - 2021",
    list("Created ShinyApp for data visualization and interactive analysis.",
         "Analyzed data and collaborated on moral psychology research.",
         "Contributed to experimental design and statistical analysis of behavioral studies."),
  "Research Assistant", "Faculty of Arts, Charles University", "Prague, Czech Republic", "2017 - 2020",
    list("Cleaned, prepared, and analyzed data from the Vysočina Cohort study.",
         "Conducted systematic reviews and meta-analyses.",
         "Contributed to longitudinal research on developmental psychology."),
  "Research Assistant", "Institute of Psychology, Czech Academy of Sciences", "Prague, Czech Republic", "2017 - 2019",
    list("Developed a similarity measure for photographs using convolutional neural networks.",
         "Implemented Python code for grid computing and conducted data analysis in R.",
         "Created norms for a Czech lexical test through data cleaning and statistical analysis.")
) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Publications

## Meta-Analysis & Publication Bias Methods

```{r publications-meta, results='asis'}
print_publications("publications-meta_analysis.bib")
```

## Statistical Methods & Theory

```{r publications-statistics, results='asis'}
print_publications("publications-statistics.bib")
```

## Empirical Research & Meta-Science

```{r publications-empirical, results='asis'}
print_publications("publications-empirical.bib")
```

## Other Publications

```{r publications-other, results='asis'}
print_publications("publications-all.bib")
```

## Other Preprints

```{r publications-preprints, results='asis'}
print_publications("publications-preprints.bib")
```

# Software

\begin{cvparagraph}
My research output includes the development of open-source R packages for statistical analysis. These packages enable scientific practitioners to apply the developed methodology in practice.
\end{cvparagraph}

```{r software, results='asis'}
software_packages <- tribble(
  ~ name, ~ url, ~ description,
  "RoBMA",      "https://cran.r-project.org/package=RoBMA",      "Robust Bayesian Meta-Analysis",
  "zcurve",     "https://cran.r-project.org/package=zcurve",     "Z-Curve 2.0: Estimating Replication Rates and Discovery Rates",
  "BayesTools", "https://cran.r-project.org/package=BayesTools", "Tools for Bayesian Analyses",
  "IRR2FPR",    "https://cran.r-project.org/package=IRR2FPR",    "IRR2FPR: Computing False Positive Rate from Inter-Rater Reliability",
  "RoBSA",      "https://cran.r-project.org/package=RoBSA",      "Robust Bayesian Survival Analysis",
  "RoBTT",      "https://cran.r-project.org/package=RoBTT",      "Robust Bayesian T-Test",
  "Meta-Analysis (JASP)",  "https://github.com/jasp-stats/jaspMetaAnalysis/", "Meta-Analysis Module for JASP",
  "Mixed Models (JASP)",   "https://github.com/jasp-stats/jaspSurvival/", "Survival Module for JASP",
  "Survival (JASP)",       "https://github.com/jasp-stats/jaspMixedModels/", "Mixed Models Module for JASP",
  "Learn Bayes (JASP)",    "https://github.com/jasp-stats/jaspLearnBayes", "Learn Bayes Module for JASP"
)

print_software(software_packages)
```

# Teaching

```{r teaching, results='asis'}
teaching_data <- tribble(
  ~ title, ~ code, ~ campus, ~ semester, ~ role,
  "Meta-Analysis", "Graduate Course", "University of Amsterdam", "2022-2025", "Instructor/Course Coordinator",
  "Bayesian Inference for Psychology", "Graduate Course", "University of Amsterdam", "2021-2026", "Assistant",
  "Good Research Practices", "Graduate Course", "University of Amsterdam", "2021-2022", "Assistant",
  "Statistická analýza dat (Statistical analysis of data)", "Graduate Course", "Faculty of Arts, Charles University", "2019-2020", "Teaching Assistant",
  "New Statistics and Other Actual Trends in Applied Data Analysis", "Graduate Course", "Faculty of Arts, Charles University", "2019-2020", "Teaching Assistant",
  "Introduction to Bayesian data analysis", "Guest Lecture", "Faculty of Arts, Charles University", "2018", "Lecturer",
  "Výzkumný seminář v experimentální sociální psychologii (Research Seminar in Experimental Social Psychology)", "Undergraduate Course", "Faculty of Arts, Charles University", "2018-2019", "Teaching Assistant"
)

print_teaching(teaching_data)
```

# Supervision

```{r supervision, results='asis'}
supervision_data <- tribble(
  ~ year, ~ type, ~ title, ~ description, ~ campus,
  "2024-2025", "Bachelor's Thesis", "A Stefanów, M Serry, O Piestrak, E Koskinen, W Brenner", "When are Bayesians going to take over the world? Literature review of Bayesian statistics in psychological research", "University of Amsterdam",
  "2022-2023", "Bachelor's Thesis", "A Sahrani, D Klein Leunk, PY Gui, D Voss, K Ullah", "How fair is a fair coin flip (published as Fair coins tend to land on the same side they started: Evidence from 350,757 flips)", "University of Amsterdam"
)

print_supervision(supervision_data)
```

# Talks \& Workshops

## Invited

```{r talks, results='asis'}
talks_data <- tribble(
  ~ when, ~ title, ~ details, ~ where,
  "2025", "Bayesian hypothesis testing: Concepts, benefits, and practical implementation", "Seminar in Advanced Research Methods", "Department of Psychology, Princeton \\href{https://princeton.zoom.us/rec/share/Sfeuxq_gcHWQH7wktYydjZytlNvQTx7yrRVjl0fcf8sCG7251CQDAI7QJX2j5K0Z.ajG6QNxxHiSgkWWu}{[recording]}",
  "2025", "Bayesian methods workshop", "Statistics \\& Methodology Platform", "Swiss Clinical Trial Organisation (SCTO), Bern",
  "2025", "Ig Nobel night", "", "Nemo, Amsterdam",
  "2025", "Ig Nobel night", "", "EPFL, Lausanne",
  "2024", "Analyzing data with JASP: A free, open-source, and user-friendly statistical software", "Methods for Evidence Synthesis Salon", "University of Bristol; remote",
  "2023", "Analyzing data with JASP: A free, open-source, and user-friendly statistical software", "", "Department of Statistics, Texas A\\&M College Station",
  "2023", "Accounting for publication bias with robust Bayesian meta-analysis", "Statistical and Machine Learning Approaches for the Social Sciences", "University of Washington; remote",
  "2022", "Informed Bayesian (model-averaged) survival analysis", "", "International Society For Clinical Biostatistics: ČR; remote",
  "2022", "Robust Bayesian meta-analysis", "", "University of Groningen; remote",
  "2021", "Bayesian meta-analysis with JASP", "", "DE-PASS; remote"
)

print_talks(talks_data)
```

## Talks 

```{r conference-talks, results='asis'}
conference_talks_data <- tribble(
  ~ year, ~ title, ~ conference, ~ place,
  "2025", "Fast and efficient robust Bayesian meta-analysis with spike-and-slab priors", "International Meeting of Psychometric Society", "Minneapolis",
  "2025", "Fast and efficient robust Bayesian meta-analysis with spike-and-slab priors", "Society for Research Synthesis Methodology", "Madison",
  "2024", "Meta-analysis with JASP", "Society for Research Synthesis Methodology", "Amsterdam",
  "2024", "Bayesian model-averaged analysis of 350,757 coin flips", "Joint Statistical Meeting", "Portland",
  "2023", "Exploring open science practices in behavioural public policy research", "MAER-NET", "Palma de Mallorca",
  "2023", "Bayesian location-scale model for assessing reliability differences with ordinal ratings", "International Meeting of Psychometric Society", "Baltimore",
  "2023", "Robust Bayesian meta-regression: Publication bias adjusted moderator analysis", "MathPsych/ICCM/EMPG", "Amsterdam",
  "2023", "Adjusting for Risk of Bias in medical meta-analyses: A large-scale analysis of Cochrane Database of Systematic Reviews", "Society for Research Synthesis Methodology", "Paris",
  "2022", "Tutorial on robust Bayesian meta-analysis in JASP and R", "MAER-NET", "Kyoto",
  "2022", "Adjusting for publication bias with Bayesian model-averaging and the RoBMA R package", "ESMARConf", "Online",
  "2021", "No need to choose: Robust Bayesian meta-analysis", "MAER-NET", "Piraeus",
  "2021", "Extending RoBMA with PET-PEESE: Mitigating publication bias with Bayesian model averaging", "International Meeting of Psychometric Society", "Online",
  "2021", "No need to choose: Extending robust Bayesian meta-analysis by model-averaging across different publication selection models", "Quantitative Analysis of Publication Bias", "Konstanz",
  "2021", "Robust Bayesian meta-analysis: A framework for addressing publication bias with model-averaging", "Seminar in psychometrics", "Prague",
  "2019", "A minority deliberately cheats for one's own and other's benefit: An investigation of dicehonesty using mouse tracking", "Prague Conference on Behavioral Sciences", "Prague",
  "2019", "Jak měřit podobnost fotografií pomocí neuronových sítí?", "Kognitivní škola", "Malá Skála",
  "2018", "Recognition of abilities in random noise: People are willing to pay for the illusion of success", "Prague Conference on Behavioral Sciences", "Prague"
)

print_conference_talks(conference_talks_data)
```

## Workshops 

```{r workshops-talks, results='asis'}
workshops_data <- tribble(
  ~ year, ~ title, ~ place,
  "2025", "State-of-the-art meta-analysis using JASP", "Amsterdam",
)

print_workshops(workshops_data)
```

# Funding, Awards \& Scholarships

## Funding

```{r funding, results='asis'}
funding_data <- tribble(
  ~ year, ~ type, ~ title, ~ amount, ~ coauthors, ~ agency,
  "2024", "Valorisation Grant", "Enabling Meta-Analytic SEM via JASP", "9.955 EUR", "together with S Jak and M Cheung", "Social and Behavioural Data Science Centre, University of Amsterdam"
)

print_funding(funding_data)
```

## Awards

```{r awards, results='asis'}
awards_data <- tribble(
  ~ award, ~ project, ~ from, ~ year,
  "Student Travel Award",                        "",  "International Meeting of Psychometric Society", "2025",
  "Ig Nobel Prize in Probability",               "For Fair coins tend to land on the same side they started: Evidence from 350,757 flips", "Ig Nobel Awards", "2024",
  "OSCAwards for Transparency, Metascience, Preregistration, and Reproducibility", "For A 27-country test of communicating the scientific consensus on climate change, together with B Većkalov and SJ Geiger", "Open Science Community Amsterdam", "2024",
  "Pineapple Science Award: Mathematics Award" , "For Fair coins tend to land on the same side they started: Evidence from 350,757 flips", "Pineapple Science Awards", "2023",
  "Travel Award",                                "", "International Society for Bayesian Analysis", "2022"
)

print_awards(awards_data)
```

## Scholarships

```{r scholarships, results='asis'}
scholarships_data <- tribble(
  ~ scholarship, ~ project, ~ from, ~ year,
  "COST Action Virtual Mobility Grant",       "For Performing (Bayesian) meta-analysis with JASP", "COST Action CA19101", "2022",
  "Doktorandská prémie ISCB ČR",              "For Informed Bayesian (model averaged) survival analysis", "International Society For Clinical Biostatistics: ČR", "2022",
  "Student Scientific Scholarship",           "For project Rozvoj metody z-curve pro odhadováni důvěryhodnosti vědeckých studií (Development of z-curve for estimation of trustworthiness of research)", "Faculty of Arts, Charles University", "2019",
  "Specific University Research Scholarship", "For project Porovnání metod pro odhad rozdílů ve shodách posuzovatelů (Comparison of methods for estimating differences in inter-rater reliability)", "Faculty of Arts, Charles University", "2019",
  "Student Scientific Scholarship",           "For project Můžeme důvěřovat výzkumům o podvádění? (Can we trust research on lying)", "Faculty of Arts, Charles University", "2018",
  "Scholarship of Special Consideration",     "For active participation at Society for Judgement and Decision making, New Orleans", "Faculty of Arts, Charles University", "2018",
  "Scholarship of Special Consideration",     "For active participation at StanCon Helsinky", "Faculty of Arts, Charles University", "2018",
  "Merit Scholarship",                        "", "Faculty of Arts, Charles University", "2017",
  "Merit Scholarship",                        "", "Faculty of Arts, Charles University", "2016"
)

print_scholarships(scholarships_data)
```

# Service

## Organization

```{r service-entries, results='asis'}
service_data <- tribble(
  ~ year, ~ title, ~ description,
  "2025", "Discovering Statistics using JASP", "Together with H Godmann, J van Doorn, and EJ Wagenmakers part of the organizing committee for the workshop. The hybrid workshop is scheduled to take place June 30, 2025.",
  "2025", "State-of-the-Art Meta-Analysis using JASP", "Together with H Godmann and EJ Wagenmakers, part of the organizing committee for the workshop. The hybrid workshop is scheduled to take place July 1, 2025.",
  "2025", "A Crash Course in Machine Learning with JASP", "Together with Henrik Godmann, D van den Bergh, K Derks, and EJ Wagenmakers, part of the organizing committee for the workshop. The hybrid workshop is scheduled to take place July 2, 2025.",
  "2025", "11th Annual JASP Workshop: Theory and Practice of Bayesian Hypothesis Testing", "Together with H Godmann, R Morey, and EJ Wagenmakers, part of the organizing committee for the two-day workshop. The hybrid workshop is scheduled to take place July 3-4, 2025.",
  "2025", "Journal of Robustness Reports", "Together with A Sarafoglou, B Aczel, S Hoogeveen, C Chambers, and EJ Wagenmakers, founded the diamond open access Journal of Robustness Reports (https://scipost.org/JRobustRep/about). Fellow of the Editorial College for the Journal of Robustness Reports, 2025-present.",
  "2024", "10th Annual JASP Workshop: Theory and Practice of Bayesian Hypothesis Testing", "Together with H Godmann, R Morey, and EJ Wagenmakers part of the organizing committee for the two-day workshop. The hybrid workshop took place July 15-16, 2024, and attracted 47 participants.",
  "2024", "12th Annual JAGS and Stan Workshop: Bayesian Modeling for Cognitive Science", "Together with H Godmann, M Lee, and EJ Wagenmakers, part of the organizing committee for the one-week workshop. The workshop took place July 8-12, 2024, in Amsterdam, the Netherlands, and attracted 20 participants.",
  "2023", "9th Annual JASP Workshop: Theory and Practice of Bayesian Hypothesis Testing", "Together with F Aust, C Guazzone, Š Kucharský, J van Doorn, R Morey, and EJ Wagenmakers, part of the organizing committee for the two-day workshop. The hybrid workshop took place July 15-16, 2023, and attracted 55 participants.",
  "2023", "11th Annual JAGS and Stan Workshop: Bayesian Modeling for Cognitive Science", "Together with F Aust, C Guazzone, M Villarreal, L Montgomery, Š Kucharský, D van den Bergh, J van Doorn, M Lee, and EJ Wagenmakers, part of the organizing committee for the one-week workshop. The workshop took place July 10-14, 2023, in Amsterdam, the Netherlands, and attracted 37 participants.",
  "2022", "8th Annual JASP Workshop: Theory and Practice of Bayesian Hypothesis Testing", "Together with L Lengersdorff, F Aust, A Sarafoglou, J Petter, S Kucharský, A Stefan, D van den Bergh, R Morey, and Eric-Jan Wagenmakers, part of the organizing committee for the two-day workshop. The hybrid workshop took place August 29-30, 2022 and attracted 55 participants.",
  "2022", "10th Annual JAGS and Stan Workshop: Bayesian Modeling for Cognitive Science", "Together with L Lengersdorff, F Aust, A Sarafoglou, M Villarreal, L Montgomery, J Petter, Š Kucharský, A Stefan, J van Doorn, M Lee, and EJ Wagenmakers, part of the organizing committee for the one-week workshop. The workshop took place August 22-26, 2022, in Amsterdam, the Netherlands, and attracted 25 participants."
)

print_service(service_data)
```

## Peer Review

```{r peer-review, results='asis'}
peer_review_data <- tribble(
  ~ journal,
  "Advances in Methods and Practices in Psychological Science",
  "Atherosclerosis",
  "Behavior Research Methods",
  "BMC Medical Research Methodology",
  "Collabra",
  "Current Medical Research and Opinion",
  "Energy Economics",
  "Health Psychology",
  "International Review of Sport and Exercise Psychology",
  "Meta-Psychology",
  "Nature Human Behaviour",
  "Personality \\& Social Psychology Bulletin",
  "PloS One",
  "Psychological Methods",
  "Research Synthesis Methods",
  "Statistics in Medicine"
)

print_peer_review(peer_review_data)
```
