---
name: 
surname: František Bartoš
date: "`r format(Sys.time(), '%B, %Y')`"
position: "Postdoctoral Researcher, CFO of JASP Services"
address: "Amsterdam, Netherlands"
email: "f.bartos96@gmail.com"
www: "frantisek-bartos.info/"
github: "FBartos"
linkedin: "franti%C5%A1ek-barto%C5%A1-50249b192/"
headcolor: "414141"
csl: apa.csl
output: 
  vitae::awesomecv:
    keep_tex: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(vitae)
source("_functions.R")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Publications

## Meta-Analysis & Publication Bias Methods

```{r publications-meta, results='asis'}
print_publications("publications-meta_analysis.bib")
```

## Statistical Methods & Theory

```{r publications-statistics, results='asis'}
print_publications("publications-statistics.bib")
```

## Empirical Research & Meta-Science

```{r publications-empirical, results='asis'}
print_publications("publications-empirical.bib")
```

## Other Publications

```{r publications-other, results='asis'}
print_publications("publications-all.bib")
```

## Other Preprints

```{r publications-preprints, results='asis'}
print_publications("publications-preprints.bib")
```

# Software

\begin{cvparagraph}
My research output includes the development of open-source R packages for statistical analysis. These packages enable scientific practitioners to apply the developed methodology in practice.
\end{cvparagraph}

```{r software, results='asis'}
print_software(read_csv("software.csv", show_col_types = FALSE))
```
